Normalization: A pipeline to analyse time-course gene expression data

### 2019-02-19 scripts/01_quality_control_normalization.Rmd
FIX saving temporary results
Attempting to add colors

```{r echo=FALSE, results="hide"}
# Loading dependencies
library(devtools)
library(limma)
library(splines)
library(stats)
library(moanin)

@@

targets = readTargets()
RG = read.maimages(
  targets, source="agilent",
  path="data/shoemaker2015/rawdata",
  other.columns="gIsWellAboveBG",
  green.only=TRUE)

@@

write.table(data, "results/quantile_normalized.txt")

@@

data_corr = cor(data, method="spearman")
aheatmap(data_corr,
         Colv=NA, Rowv=NA,
         annCol=meta[,
		     c("Group", "Time",
			"Replicate")],
         annLegend=FALSE, 
         main="Replicates\nAfter Normalization")
```

>>>>

```{r echo=FALSE, results="hide"}
# Loading dependencies
library(devtools)
library(limma)
library(splines)
library(stats)
library(moanin)
source("utils.R")

@@

targets = readTargets()
RG = read.maimages(
  targets, source="agilent",
  path="data/shoemaker2015/rawdata",
  other.columns="gIsWellAboveBG",
  green.only=TRUE)
```

@@

write.table(data, ".results/quantile_normalized.txt")

@@

data_corr = cor(data, method="spearman")
aheatmap(data_corr,
         Colv=NA, Rowv=NA,
         annCol=meta[,
		     c("Group", "Time",
			"Replicate")],
         annLegend=FALSE, 
	 annColors=ann_colors,
         main="Replicates\nAfter Normalization")
```
